\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-10-21 metatheory-condensed.tex
More questions

$$
\Rule[]
{}
{\goodWSig{\Gamma}{w\cdot}{0}}
\quad
\Rule[name=WSig-Add]
{\goodWSig{\Gamma}{\tau}{n}
  \quad \goodType{\Gamma}{A}{i}
  \quad \goodType{\Gamma, A}{B}{i}}
{\goodWSig{\Gamma}{w^+ \  \tau \  A \  B}{n+1}}
\quad
\Rule[name=Ind-Univ]
{\goodWSig{\Gamma}{\tau}{n}}
{\goodType{\Gamma}{\bW \tau}{i}
}
$$
$$
\Rule[name=Ind-Term]
{\goodTerm{\Gamma}{T}{\bW \tau}
  \quad \goodTerm{\Gamma}{a}{\pi^j_1\tau}
  \quad \goodTerm{\Gamma, \pi^j_2\tau[(id, a)]}{b}{El~("W"~T)}}
{\goodTerm{\Gamma}{"Wsup"~T~a~b}{El~("W"~T)} }
$$
$$
\Rule[name=Hdler]
{\goodType{\Gamma}{A}{}
\quad \goodType{\Gamma, A}{B}{}
\quad \goodType{\Gamma}{R}{}
}
{\goodType{\Gamma}{"RecSig1"~A~B~R \equiv \Pi A\; \Pi (\Pi B (R[\pi_1\circ\pi_1]))\; R[\pi_1\circ\pi_1]}{}}
\quad 
\Rule[name=Hdlers]
{\goodWSig{\Gamma}{\tau}{n}
\quad \goodType{\Gamma}{R}{}
}
{\goodSig{\Gamma}{"RecSig"~\tau~R}{n}}
$$
$$
\Rule[name=Hdler-Proj]
{ \goodWSig{\Gamma}{\tau}{N}
\quad \goodTerm{\Gamma}{o}{\cL("RecSig"~\tau~R)}
\quad j < N
}
{\goodTerm{\Gamma}{"prjR"~j~o}{("RecSig1"~(\pi_1^j \tau)~(\pi_2^j \tau)~R)[\pi_1]}}\YZ{Why is this pi_1 substitution needed?}
$$
$$
\Rule[name=Rec-Constr]
{ \goodWSig{\Gamma}{\tau}{N}
\quad \goodTerm{\Gamma}{T}{\bW \tau}
\quad \goodType{\Gamma}{R}{}
\quad \goodTerm{\Gamma}{r}{\cL("RecSig"~\tau~R)}
\quad \goodTerm{\Gamma}{w}{El~("W"~T)}\YZ{Is the 1st premise implied by the 2nd, and the 3rd implied by the 4th?}
}
{\goodTerm{\Gamma}{"Wrec"~r~w}{R}}
$$

>>>>

$$
\Rule[]
{}
{\goodWSig{\Gamma}{w\cdot}{0}}
\quad
\Rule[name=WSig-Add]
{\goodWSig{\Gamma}{\tau}{n}
  \quad \goodType{\Gamma}{A}{i}
  \quad \goodType{\Gamma, A}{B}{i}}
{\goodWSig{\Gamma}{w^+ \  \tau \  A \  B}{n+1}}
\quad
\Rule[name=Ind-Univ]
{\goodWSig{\Gamma}{\tau}{n}}
{\goodType{\Gamma}{\bW \tau}{i}
}
$$
$$
\Rule[name=Ind-Term]
{\goodTerm{\Gamma}{T}{\bW \tau}
  \quad \goodTerm{\Gamma}{a}{\pi^j_1\tau}
  \quad \goodTerm{\Gamma, \pi^j_2\tau[(id, a)]}{b}{El~("W"~T)}}
{\goodTerm{\Gamma}{"Wsup"~T~a~b}{El~("W"~T)} }
$$
$$
\Rule[name=Hdler]
{\goodType{\Gamma}{A}{}
\quad \goodType{\Gamma, A}{B}{}
\quad \goodType{\Gamma}{R}{}
}
{\goodType{\Gamma}{"RecSig1"~A~B~R \equiv \Pi A\; \Pi (\Pi B (R[\pi_1\circ\pi_1]))\; R[\pi_1\circ\pi_1]}{}}
\quad 
\Rule[name=Hdlers]
{\goodWSig{\Gamma}{\tau}{n}
\quad \goodType{\Gamma}{R}{}
}
{\goodSig{\Gamma}{"RecSig"~\tau~R}{n}}
$$
$$
\Rule[name=Hdler-Proj]
{ \goodWSig{\Gamma}{\tau}{N}
\quad \goodTerm{\Gamma}{o}{\cL("RecSig"~\tau~R)}
\quad j < N
}
{\goodTerm{\Gamma}{"prjR"~j~o}{("RecSig1"~(\pi_1^j \tau)~(\pi_2^j \tau)~R)[\pi_1]}}\YZ{Why is this pi_1 substitution needed?}
$$
$$
\Rule[name=Rec-Constr]
{ \goodWSig{\Gamma}{\tau}{N}
\quad \goodTerm{\Gamma}{T}{\bW \tau}
\quad \goodType{\Gamma}{R}{}
\quad \goodTerm{\Gamma}{r}{\cL("RecSig"~\tau~R)}
\quad \goodTerm{\Gamma}{w}{El~("W"~T)}\YZ{Is the 1st premise implied by the 2nd, and the 3rd implied by the 4th?}
}
{\goodTerm{\Gamma}{"Wrec"~r~w}{R}}\YZ{I suppose Rec-Constr is only for exhaustivity checking? If so, then would it be more intuitive to not include the w in the term? And I suppose the programmer will want to use sealing to hide its type, or otherwise it would fail to normalize for lack of a beta rule?}
$$

### 2022-10-21 syntax.tex
More questions

$$
\Rule[name=Lnkg Proj]
{\goodTerm{\Gamma}{o}{\cL\sigma}}
{\goodTerm{\Gamma}{p_1\mu \ o}{\cL (p_1\nu \ \sigma)}
\\ \goodTerm{\Gamma, p_1\nu' \ \sigma}{p_2\mu \ o}{p_2\nu \ \sigma}
}
\quad 
\Rule[name=Lnkg Compile]
{ \goodTerm{\Gamma}{o}{\cL \sigma} 
}
{
  \goodTerm{\Gamma}{\cCt o}{\cC \sigma}
}
$$
$$ 
\Rule[name=Lnkg Proj Beta]
{\goodTerm{\Gamma}{o}{\cL \sigma} 
\quad \goodType{\Gamma}{A}{}
\quad  \goodSeal{\Gamma}{f}{\sigma}{A} 
 \quad \goodTerm{\Gamma, A}{t}{T}}
{\goodTerm{\Gamma}{p_1\mu \ (\mu^+ \ o \ \{f\} \ t) \equiv o}{\cL \sigma}
\\ \goodTerm{\Gamma, A}{p_2\mu \  (\mu^+ \ o \ \{f\} \ t) \equiv t}{T}
}
$$
$$
\Rule[name=Compile]
{}
{\goodType{\Gamma}{\cC \nu\cdot \equiv \top}{} 
\\
\goodType{\Gamma}{\cC (\nu^+ \ \sigma \ \{f\} \ T) \equiv 
    \Sigma (\cC \sigma) T["sf" \ f]}{}
\\\\ \goodTerm{\Gamma}{ \cCt \mu\cdot \equiv ()}{\cC \nu\cdot}
\\ \goodTerm{\Gamma}{\cCt \ (\mu^+ \ o \ \{f\}\ t) \equiv ((\cCt \ o), t["sf" \ f][(id, \cCt \ o)]) }{}\YZ{nothing after colon?}\EDJreply{There should be something but the space is not enough.}
}
$$
% $$
% \Rule
% { \goodSeal{\Gamma}{f}{\sigma}{A}
% \\ \goodType{\Gamma, A}{T}{}
% \\ \goodTerm{\Gamma}{t}{T}
% }{}
% $$

@@

\YZ{sf' seems unnecessary, since sf' s ad s are the same?}\EDJreply{Yes. Technically it is pretty unnecessary. It is just a bit weird to have $\goodTerm{\Gamma, \cC \sigma}{s}{A[\pi_1]}$ and $\goodSeal{\Gamma}{s}{\sigma}{A}$ at the same time because it is one derivation but turns out to be two judgements, for intrinsically typed. I can also remove ``sf'' if you don't find it weird. I initially having ``sf'' to just *emphasize* ``sf s'' should be considered as a term  and ``s'' a sealing}\YZreply{
  I'm still confused about the difference among s, sf s and sf' s.
  I thought s and sf' s were technically the same; they are both terms of type A[pi1] in a context that contains cC sigma.
  I thought sf s was different because it is a substitution.
}\EDJreply{You are absolutely right. s and sf' s are techincally the same. sf s is a substitution.
  About s and sf' s, I can say that, I don't allow something like $\goodSeal{\Gamma}{sf'~s}{\sigma}{A}$. The reason I don't allow it is only notational consideration. 
  I mean technically we can consider them the same. I can just remove all the appearances of sf' if you want and find it less confusing.
}\YZreply{Yes, sf' is confusing to me.}\EDJreply{sf' notation removed. Please check.}
Note that, given $\goodSeal{\Gamma}{s}{\sigma}{A} = \goodTerm{\Gamma, \cC\sigma}{s}{A}$, notation "sf"
(used in \ruleref{Compile}) is defined as the substitution $\goodSub{\Gamma,
\cC \sigma}{(sf~s) \coloneqq (\pi_1, s)}{\Gamma, A}$.

@@

Now, together with sealing, we can read \ruleref{Sig Add} and
\ruleref{Lnkg Add} out clearly: given a constructed linkage $o : \cL\sigma$
of signature $\sigma$, the next added field $t : T$ will have
to be in the context of the abstraction $A$\YZ{Why do Lnkg Add and Sig Add leave A unspecified? I thought this A corresponds to 'self'.}\EDJreply{You are asking where is the function \cC \{a : \bW sigma ; ..\} to \cC\{a : \cU ; ..\}, which by definition is requesting (Sigma (a : \bW sigma ; ..)) to (Sigma (a : \cU ; ..)). \\
This is something doable in vanilla MLTT, with the help of transforming \bW sigma to \cU, by rule `Ind-Type'. And this function's type should be directly the sealing type.}\YZreply{
  My confusion is this: it seems that in Lnkg Add and Sig Add, A could well be the top type and f a value of the top type. In this sense, A seems unspecified.
  Or maybe in the metatheory, it is the programmer's responsibility to find this A?
}\EDJreply{You are absolutely right. In metatheory it is programmer's responsibility to specify the A they want. If they set A to top, they can do that but it will be hard for them to achieve meaningful program. \\
Also the `f' is specified together with `A' by the user as well. \\
A bit off-topic : this is not the only place that such specification is postponed to the user (in metatheory) another place is in inheritance when specifying upcasting function.}
of the compilation $\cC\sigma$ (witnessed by the seal $f$).
The ``concatenation'' of the
$o$ and $t$ leads to a new linkage, of which the signature is the
``concatenation'' of the $\sigma$ and $T$ (we also record the sealing
$f$ for simplicity). The key here is our signature, will \textit{record}
this abstraction witness $f$,
%\YZ{Why is it necessary to record the witness f? I don't see how p_f nu is needed anywhere.}\EDJreply{1. this is for the sake of eta/beta rule (local soundness + local completeness); 2.It is actually used in the rule Compile (the last one), if Ct is compile a variable, say ``Ct v'', then this ``Ct v = (Ct p_1 v), (t[sf p_f v][...])'', the f will actually be replaced by p_f; 3. p_f can be used by the user. It doesn't have to interact with other typing rules. }
thus any projected member will still be in
the abstracted context and thus possibly \textit{inheritable}.  The
construction of linkage in \ruleref{Lnkg Add} requires $t$ to
\textbf{only} refer to the (abstraction $A$ of) former part of the
defining family $o : \cL\sigma$, this is to avoid inconsistency
mentioned in \ref{chg:consistency} in metatheory.

@@

$$
\Rule[name=Hdler]
{\goodType{\Gamma}{A}{}
\quad \goodType{\Gamma, A}{B}{}
\quad \goodType{\Gamma}{R}{}
}
{\goodType{\Gamma}{"RecSig1"~A~B~R \equiv (\Pi A (\Pi (\Pi B (R[\pi_1\circ\pi_1])) R[\pi_1\circ\pi_1]) )}{}}
\quad 
\Rule[name=Hdlers]
{\goodWSig{\Gamma}{\tau}{n}
\quad \goodType{\Gamma}{R}{}
}
{\goodSig{\Gamma}{"RecSig"~\tau~R}{n}}
$$
$$
\Rule[name=Hdler-Proj]
{ \goodWSig{\Gamma}{\tau}{N}
\quad \goodTerm{\Gamma}{o}{\cL("RecSig"~\tau~R)}
\quad j < N
}
{\goodTerm{\Gamma}{"prjR"~j~o}{("RecSig1"~(\pi_1^j \tau)~(\pi_2^j \tau)~R)[\pi_1]}}
$$
$$
\Rule[name=Rec-Constr]
{ \goodWSig{\Gamma}{\tau}{N}
\quad \goodTerm{\Gamma}{T}{\bW \tau}
\quad \goodType{\Gamma}{R}{}
\quad \goodTerm{\Gamma}{r}{\cL("RecSig"~\tau~R)}
\quad \goodTerm{\Gamma}{w}{El~("W"~T)}
}
{\goodTerm{\Gamma}{"Wrec"~r~w}{R}}\YZ{
(1) Use \tau for inductive types and \sigma for linkage signatures.
(2) Try using the same metavariables (j and n) as in the rules on W-types.
(3) In Rec-Constr, no checking of \Gamma \vdash T : \bW \tau?
(4) Why are RecSig1, RecSig, Wrec, prjR not listed in the syntax figure?
}\EDJreply{Thx. Working on it. I seem to forgot to add inheritance as well.}\EDJreply{Done. Please Check.}
$$

@@

$$
\Rule[name=Inh-Ext]
{\goodInh{\Gamma}{h}{\sigma_1}{\sigma_2}
  \quad \goodTerm{\Gamma, A_2}{t}{T}}
{\goodInh{\Gamma}{"inhext" \ h \ t}{\sigma_1}{(\nu^+ \  \sigma_2\  T)}}
\quad
\Rule[name=Inh-Inh]
{\goodInh{\Gamma}{h}{\sigma_1}{\sigma_2}
\quad \goodType{\Gamma, A_1}{T}{}
\quad \goodTerm{\Gamma, A_2}{\uparrow^s}{A_1[\pi_1]}
}
{\goodInh{\Gamma}{"inhinh" \ h}{(\nu^+ \  \sigma_1 \  T)}{(\nu^+ \  \sigma_2 \  T[(\pi_1, \uparrow^s)])}}
$$
$$
\Rule[name=Inh]
{\goodInh{\Gamma}{h}{\sigma_1}{\sigma_2}
\quad \goodTerm{\Gamma}{l}{\cL \sigma_1}
}
{\goodTerm{\Gamma}{("inh" \ h \ l)}{\cL \sigma_2}} 
\quad
\Rule[name=Inh+Inh]
{\goodInh{\Gamma}{h}{\sigma_1}{\sigma_2}
\quad \goodTerm{\Gamma, A_2}{\uparrow^s}{A_1[\pi_1]}
\\\\
\goodInh{\Gamma, A_2}{i}{\tau_1[(\pi_1, \uparrow^s)]}{\tau_2}}
{\goodInh{\Gamma}{"inhnest" \ h \ i}{(\nu^+ \  \sigma_1\  \cL\tau_1)}{(\nu^+ \  \sigma_2\  \cL\tau_2)}}
\quad
$$

>>>>

$$
\Rule[name=Lnkg Proj]
{\goodTerm{\Gamma}{o}{\cL\sigma}}
{\goodTerm{\Gamma}{p_1\mu \ o}{\cL (p_1\nu \ \sigma)}
\\ \goodTerm{\Gamma, p_1\nu' \ \sigma}{p_2\mu \ o}{p_2\nu \ \sigma}
}
\quad 
\Rule[name=Lnkg Compile]
{ \goodTerm{\Gamma}{o}{\cL \sigma} 
}
{
  \goodTerm{\Gamma}{\cCt o}{\cC \sigma}
}
$$
$$ 
\Rule[name=Lnkg Proj Beta]
{\goodTerm{\Gamma}{o}{\cL \sigma} 
\quad \goodType{\Gamma}{A}{}
\quad  \goodSeal{\Gamma}{f}{\sigma}{A} 
 \quad \goodTerm{\Gamma, A}{t}{T}}
{\goodTerm{\Gamma}{p_1\mu \ (\mu^+ \ o \ \{f\} \ t) \equiv o}{\cL \sigma}
\\ \goodTerm{\Gamma, A}{p_2\mu \  (\mu^+ \ o \ \{f\} \ t) \equiv t}{T}
}
$$
$$
\Rule[name=Compile]
{}
{\goodType{\Gamma}{\cC \nu\cdot \equiv \top}{} 
\\
\goodType{\Gamma}{\cC (\nu^+ \ \sigma \ \{f\} \ T) \equiv 
    \Sigma (\cC \sigma) T["sf" \ f]}{}
\\\\ \goodTerm{\Gamma}{ \cCt \mu\cdot \equiv ()}{\cC \nu\cdot}
\\ \goodTerm{\Gamma}{\cCt \ (\mu^+ \ o \ \{f\}\ t) \equiv ((\cCt \ o), t["sf" \ f][(id, \cCt \ o)]) }{}
}
$$
% $$
% \Rule
% { \goodSeal{\Gamma}{f}{\sigma}{A}
% \\ \goodType{\Gamma, A}{T}{}
% \\ \goodTerm{\Gamma}{t}{T}
% }{}
% $$

@@

%\YZ{sf' seems unnecessary, since sf' s ad s are the same?}\EDJreply{Yes. Technically it is pretty unnecessary. It is just a bit weird to have $\goodTerm{\Gamma, \cC \sigma}{s}{A[\pi_1]}$ and $\goodSeal{\Gamma}{s}{\sigma}{A}$ at the same time because it is one derivation but turns out to be two judgements, for intrinsically typed. I can also remove ``sf'' if you don't find it weird. I initially having ``sf'' to just *emphasize* ``sf s'' should be considered as a term  and ``s'' a sealing}\YZreply{
%  I'm still confused about the difference among s, sf s and sf' s.
%  I thought s and sf' s were technically the same; they are both terms of type A[pi1] in a context that contains cC sigma.
%  I thought sf s was different because it is a substitution.
%}\EDJreply{You are absolutely right. s and sf' s are techincally the same. sf s is a substitution.
%  About s and sf' s, I can say that, I don't allow something like $\goodSeal{\Gamma}{sf'~s}{\sigma}{A}$. The reason I don't allow it is only notational consideration. 
%  I mean technically we can consider them the same. I can just remove all the appearances of sf' if you want and find it less confusing.
%}\YZreply{Yes, sf' is confusing to me.}\EDJreply{sf' notation removed. Please check.}
Note that, given $\goodSeal{\Gamma}{s}{\sigma}{A} = \goodTerm{\Gamma, \cC\sigma}{s}{A}$, notation "sf"
(used in \ruleref{Compile}) is defined as the substitution $\goodSub{\Gamma,
\cC \sigma}{(sf~s) \coloneqq (\pi_1, s)}{\Gamma, A}$.

@@

Now, together with sealing, we can read \ruleref{Sig Add} and
\ruleref{Lnkg Add} out clearly: given a constructed linkage $o : \cL\sigma$
of signature $\sigma$, the next added field $t : T$ will have
to be in the context of the abstraction $A$
% \YZ{Why do Lnkg Add and Sig Add leave A unspecified? I thought this A corresponds to 'self'.}\EDJreply{You are asking where is the function \cC \{a : \bW sigma ; ..\} to \cC\{a : \cU ; ..\}, which by definition is requesting (Sigma (a : \bW sigma ; ..)) to (Sigma (a : \cU ; ..)). \\
% This is something doable in vanilla MLTT, with the help of transforming \bW sigma to \cU, by rule `Ind-Type'. And this function's type should be directly the sealing type.}\YZreply{
%   My confusion is this: it seems that in Lnkg Add and Sig Add, A could well be the top type and f a value of the top type. In this sense, A seems unspecified.
%   Or maybe in the metatheory, it is the programmer's responsibility to find this A?
% }\EDJreply{You are absolutely right. In metatheory it is programmer's responsibility to specify the A they want. If they set A to top, they can do that but it will be hard for them to achieve meaningful program. \\
% Also the `f' is specified together with `A' by the user as well. \\
% A bit off-topic : this is not the only place that such specification is postponed to the user (in metatheory) another place is in inheritance when specifying upcasting function.}
of the compilation $\cC\sigma$ (witnessed by the seal $f$).
The ``concatenation'' of the
$o$ and $t$ leads to a new linkage, of which the signature is the
``concatenation'' of the $\sigma$ and $T$ (we also record the sealing
$f$ for simplicity). The key here is our signature, will \textit{record}
this abstraction witness $f$,
%\YZ{Why is it necessary to record the witness f? I don't see how p_f nu is needed anywhere.}\EDJreply{1. this is for the sake of eta/beta rule (local soundness + local completeness); 2.It is actually used in the rule Compile (the last one), if Ct is compile a variable, say ``Ct v'', then this ``Ct v = (Ct p_1 v), (t[sf p_f v][...])'', the f will actually be replaced by p_f; 3. p_f can be used by the user. It doesn't have to interact with other typing rules. }
thus any projected member will still be in
the abstracted context and thus possibly \textit{inheritable}.  The
construction of linkage in \ruleref{Lnkg Add} requires $t$ to
\textbf{only} refer to the (abstraction $A$ of) former part of the
defining family $o : \cL\sigma$, this is to avoid inconsistency
mentioned in \ref{chg:consistency} in metatheory.

@@

$$
\Rule[name=Hdler]
{\goodType{\Gamma}{A}{}
\quad \goodType{\Gamma, A}{B}{}
\quad \goodType{\Gamma}{R}{}
}
{\goodType{\Gamma}{"RecSig1"~A~B~R \equiv (\Pi A (\Pi (\Pi B (R[\pi_1\circ\pi_1])) R[\pi_1\circ\pi_1]) )}{}}
\quad 
\Rule[name=Hdlers]
{\goodWSig{\Gamma}{\tau}{n}
\quad \goodType{\Gamma}{R}{}
}
{\goodSig{\Gamma}{"RecSig"~\tau~R}{n}}
$$
$$
\Rule[name=Hdler-Proj]
{ \goodWSig{\Gamma}{\tau}{N}
\quad \goodTerm{\Gamma}{o}{\cL("RecSig"~\tau~R)}
\quad j < N
}
{\goodTerm{\Gamma}{"prjR"~j~o}{("RecSig1"~(\pi_1^j \tau)~(\pi_2^j \tau)~R)[\pi_1]}}
$$
$$
\Rule[name=Rec-Constr]
{ \goodWSig{\Gamma}{\tau}{N}
\quad \goodTerm{\Gamma}{T}{\bW \tau}
\quad \goodType{\Gamma}{R}{}
\quad \goodTerm{\Gamma}{r}{\cL("RecSig"~\tau~R)}
\quad \goodTerm{\Gamma}{w}{El~("W"~T)}
}
{\goodTerm{\Gamma}{"Wrec"~r~w}{R}}
$$

@@

$$
\Rule[name=Inh-Ext]
{\goodInh{\Gamma}{h}{\sigma_1}{\sigma_2}
  \quad \goodTerm{\Gamma, A_2}{t}{T}}
{\goodInh{\Gamma}{"inhext" \ h \ t}{\sigma_1}{(\nu^+ \  \sigma_2\  T)}}
\quad
\Rule[name=Inh-Inh]
{\goodInh{\Gamma}{h}{\sigma_1}{\sigma_2}
\quad \goodType{\Gamma, A_1}{T}{}
\quad \goodTerm{\Gamma, A_2}{\uparrow^s}{A_1[\pi_1]}
}
{\goodInh{\Gamma}{"inhinh" \ h}{(\nu^+ \  \sigma_1 \  T)}{(\nu^+ \  \sigma_2 \  T[(\pi_1, \uparrow^s)])}}\YZ{Should the term be 'inhinh h t' instead of 'inhinh h', where t is the field being inherited?}
$$
$$
\Rule[name=Inh]
{\goodInh{\Gamma}{h}{\sigma_1}{\sigma_2}
\quad \goodTerm{\Gamma}{l}{\cL \sigma_1}
}
{\goodTerm{\Gamma}{("inh" \ h \ l)}{\cL \sigma_2}} 
\quad
\Rule[name=Inh+Inh]
{\goodInh{\Gamma}{h}{\sigma_1}{\sigma_2}
\quad \goodTerm{\Gamma, A_2}{\uparrow^s}{A_1[\pi_1]}
\\\\
\goodInh{\Gamma, A_2}{i}{\tau_1[(\pi_1, \uparrow^s)]}{\tau_2}}
{\goodInh{\Gamma}{"inhnest" \ h \ i}{(\nu^+ \  \sigma_1\  \cL\tau_1)}{(\nu^+ \  \sigma_2\  \cL\tau_2)}}
\quad
$$
